Manuscript_1

### 2025-01-30 Manuscript_1.Rmd
Update README file and fix a typo in script

###################################
#### Figure 1D SNCA locus #########
###################################
# Zoom on SNCA an add ATACseq dataof the locus
# Define parameters for a small part of chr4 where SNCA is
# Add ATACseq track of smNPC, mDAN D15, mDAN D30, mDAN D50
# text D
plotText(label = "D", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 5.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

>>>>

###################################
#### Figure 1D SNCA locus #########
###################################
# Zoom on SNCA an add ATACseq data of the locus
# Define parameters for a small part of chr4 where SNCA is
# Add ATACseq track of smNPC, mDAN D15, mDAN D30, mDAN D50
# text D
plotText(label = "D", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 4.125, 
         y = 5.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
